\problemname{Refrigerator Transport}
A factory that constructs refrigerator will deliver a shipment of $n$ refrigerator to a store.
The factory has two cars it can use:
\begin{itemize}
    \item Car A costs $p_a$ Swedish kronor per trip, and can load $k_a$ refrigerator per trip.
    \item Car B costs $p_b$ Swedish kronor per trip, and can load $k_b$ refrigerator per trip.
\end{itemize}

When transporting the refrigerator, each of the cars can be used any number of times.
Depending on how many trips each car performs, one would get a different \emph{total cost of transporting} all the refrigerator.
Your task is to write a program that takes this data and computes how many trips each car should take in order to minimize this cost.

\section*{Input}
The first and only line of input contains five integers separated by spaces:

\begin{itemize}
    \item the cost per trip $p_a$ ($500 \le p_a \le 2\,000$) of the car A,
    \item the capacity per trip $k_a$ ($10 \le k_a \le 50$) of the car A,
    \item the cost per trip $p_b$ ($500 \le p_b \le 2\,000$) of the car B,
    \item the capacity per trip $k_b$ ($10 \le k_b \le 50$) of the car, and B
    \item the number of refrigerator to transport $n$ ($1 \le n \le 1\,000$).
\end{itemize}

\section*{Output}
Output a single line with three integers -- the number of trips the first car should make, the number of trips the second car should make, and the total cost of transportation.

\section*{Scoring}
Your solution will be tested on a set of test groups, each worth a number of points.
To get the points for a test group you need to solve all test cases in the test group. Your final score will be the maximum score of a single submission.

\noindent
\begin{tabular}{| l | l | l |}
  \hline
  Group & Points & Constraints \\ \hline
  $1$    & $33$        &  Only car A should make any trips in the optimal solution. \\ \hline
  $2$    & $67$        &  No additional constraints \\ \hline
\end{tabular}
